\begin{thebibliography}{10}

\bibitem{docker_part} 
	\emph{Docker: Customers story}. {[}online] 2017 {[}cit. 2017-5-4]. Dostupné z: \url{https://www.docker.com/customers}

\bibitem{chroot}MATTEO, Riondato. 
  \emph{FreeBSD Handbook Chapter 15 Jails}. freebsd.org. The FreeBSD Project {[}online] 2014 {[}cit. 2017-1-27] Dostupné z: \url{https://www.freebsd.org/doc/en_US.ISO8859-1/books/handbook/jails.html}	
  
\bibitem{solaris_zone} 
	\emph{Solaris Internals wiki:Zones}. {[}online] 2007 {[}cit. 2017-1-27]. Dostupné z: \url{https://solarisinternals.com/wiki/index.php/Zones}	  

\bibitem{gp_38}BOTTOMLEY, James.
	\emph{WHAT IS ALL THE CONTAINER HYPE?}. {[}online] 2014 {[}cit. 2017-1-27]. Dostupné z: \url{https://virtuozzo.com/wp-content/uploads/2016/03/Virtuozzo_Container-Hype_WP_Ltr_2015_March2016.pdf}
    
\bibitem{windows_container}
	\emph{Windows Containers}. {[}online] 2016 {[}cit. 2017-2-4]. Dostupné z: \url{https://docs.microsoft.com/en-us/virtualization/windowscontainers/about/}
       
\bibitem{dotcloud_docker}GLOUB, Ben.
	\emph{DotCloud, Inc. is Becoming Docker, Inc}. {[}online] 2013 {[}cit. 2017-2-4]. Dostupné z: \url{https://blog.docker.com/2013/10/dotcloud-is-becoming-docker-inc/}

\bibitem{docker_mil}KONRAD, Alex.
	\emph{Forbes: Open-Source Darling Docker Cracks The Billion-Dollar Club With \$95 Million Raise}. {[}online] 2015 {[}cit. 2017-2-15]. Dostupné z: \url{https://www.forbes.com/sites/alexkonrad/2015/04/14/docker-raises-95-million-at-billion-valuation/}

\bibitem{cluster_vyzkum}FERRANTI, Alex.
	\emph{Survey: 96\% increase in container production usage over past year}. {[}online] 2016 {[}cit. 2017-2-17]. Dostupné z: \url{https://blog.docker.com/2013/10/dotcloud-is-becoming-docker-inc/}

\bibitem{oci_born}Open Container Initiative
	\emph{Industry Leaders Unite to Create Project for Open Container Standards}. {[}online] 2015 {[}cit. 2017-2-17]. Dostupné z: \url{https://www.opencontainers.org/announcement/2015/06/20/industry-leaders-unite-to-create-project-for-open-container-standards}

\bibitem{docker_1_12}Docker Core Engineering.
	\emph{Docker 1.12: Now with Built-in Orchestration!}. {[}online] 2016 {[}cit. 2017-3-20]. Dostupné z: \url{https://blog.docker.com/2016/06/docker-1-12-built-in-orchestration/}	


\bibitem{Docker_OD} HOLLA, Shrikrishna. 
  \emph{Orchestrating Docker}. Packt Publishing Limited, 2015, 154 s. ISBN 978-1-783-98478-7

%\bibitem{swarm_arch} Docker Documentation 
%	\emph{Docker Documentation:Swarm mode overview}. {[}online] 2016 {[}cit. 2017-XX-XX]. Dostupné z: \url{https://docs.docker.com/engine/swarm/}

\bibitem{docker_lib} HYKES, Solomon.
	\emph{Docker 0.9: introducing execution drivers and libcontainer}. {[}online]. 2014 {[}cit. 2017-3-25]. Dostupné z: \url{https://blog.docker.com/2014/03/docker-0-9-introducing-execution-drivers-and-libcontainer/}

\bibitem{coreos_00} PHILIPS, Brandon.
	\emph{rkt: initial commit}. {[}online]. 2014 {[}cit. 2017-3-27]. Dostupné z: \url{https://github.com/rkt/rkt/releases/tag/v0.0.0}

\bibitem{kube_incubator}Kubernetes komunita
	\emph{Github: Kubernetes-incubator}. {[}online]. 2016 {[}cit. 2017-3-28]. Dostupné z: \url{https://github.com/kubernetes-incubator}

\bibitem{cri_o_inc}Kubernetes komunita
	\emph{Github: Cri-o}. {[}online]. 2016 {[}cit. 2017-3-28]. Dostupné z: \url{https://github.com/kubernetes-incubator/cri-o}

\bibitem{cri_o}
	\emph{Github: Cri-o: Releases}. {[}online] 2017 {[}cit. 2017-3-28]. Dostupné z: \url{https://github.com/kubernetes-incubator/cri-o/releases/tag/v0.1}


\bibitem{beda_prez}BEDA, Joe.
	\emph{Containers At Scale}. {[}online] 2017 {[}cit. 2017-3-28]. Dostupné z: \url{https://speakerdeck.com/jbeda/containers-at-scale}	

\bibitem{docker_1_0}BARBIER, Julien.
	\emph{It’s Here: Docker 1.0}. {[}online]. 2014 {[}cit. 2017-3-28]. Dostupné z: \url{https://blog.docker.com/2014/06/its-here-docker-1-0/}

\bibitem{K8S_micro} VOHRA, Deepak. 
  \emph{Kubernetes Microservices with Docker}. Berkley, United States, 2016, 432 s. ISBN 978-1-484-21906-5

\bibitem{lb_ha}HEIDI, Erika.
	\emph{What Makes a System Highly Available?}. {[}online]. 2016 {[}cit. 2017-4-4]. Dostupné z: \url{https://www.digitalocean.com/community/tutorials/what-is-high-availability}

\bibitem{Docker_doc_layers} Docker Documentation
	\emph{Docker Documentation: Understand images, containers, and storage drivers}. {[}online] 2016 {[}cit. 2017-4-4]. Dostupné z: \url{https://docs.docker.com/engine/userguide/storagedriver/imagesandcontainers/}

\bibitem{fleet_systemd}Systemd doc tým
	\emph{systemd System and Service Manager}. {[}online] 2017 {[}cit. 2017-4-7]. Dostupné z: \url{https://www.freedesktop.org/wiki/Software/systemd/}	

\bibitem{fleet_lim}CoreOS tým
	\emph{CoreOS: fleet and scaling}. {[}online] 2016 {[}cit. 2017-4-8]. Dostupné z: \url{https://github.com/coreos/fleet/blob/master/Documentation/fleet-scaling.md}	

\bibitem{fleet_end}WOOD, Josh.
	\emph{Container orchestration: Moving from fleet to Kubernetes}. {[}online] 2017 {[}cit. 2017-4-8]. Dostupné z: \url{https://coreos.com/blog/migrating-from-fleet-to-kubernetes.html}	
  
\bibitem{swarm_compose} Docker Documentation 
	\emph{Docker Documentation:Use Compose with Swarm}. {[}online] 2016 {[}cit. 2017-4-8]. Dostupné z: \url{https://docs.docker.com/compose/swarm/}    

\bibitem{mesos} HINDMAN, Benjamin, KONWINSKI Andy, ZAHARIA, Matei, GHODSI Alii, JOSEPH D., Anthony, KATZ, Randy, SHENKER, Scoot, Stoica Ion. 
	\emph{Mesos: A Platform for Fine-Grained Resource Sharing in the Data Center}. {[}online] 2010 {[}cit. 2017-4-9]. Dostupné z: \url{http://mesos.berkeley.edu/mesos_tech_report.pdf}   

\bibitem{k8s_kuba} RENSIN, David K. 
  \emph{Kubernetes Scheduling the Future at Cloud Scale}. O'Reilly, United States, 2015, 38 s. ISBN 978-1-491-93599-6

\bibitem{Docker_learning} RAJ,  Pethuru, SINGH, Vinod, CHELLADHURAI, Jeeva S. 
  \emph{Learning Docker}. Packt Publishing Limited, 2015, 240 s. ISBN 978-1-784-39793-7

\bibitem{Docker_vs_rkt} rkt Documentationn
	\emph{rkt Documentation: rkt vs other projects}. {[}online] 2016 {[}cit. 2017-4-12]. Dostupné z: \url{https://coreos.com/rkt/docs/latest/rkt-vs-other-projects.html}

\bibitem{ngnix} W3techs tým
    \emph{W3techs: Usage of web servers for websites}. {[}online] 2015 {[}cit. 2017-4-17]. Dostupné z: \url{https://w3techs.com/technologies/overview/web_server/all}

\bibitem{ms_ms} rkt Documentationn
	\emph{Microsoft Azure - Azure Service Fabric and the Microservices Architecture}. {[}online] 2016 {[}cit. 2017-4-19]. Dostupné z: \url{https://msdn.microsoft.com/en-us/magazine/mt595752.aspx}

\bibitem{ubuntu_alpine} gliderlabs/docker-alpine
	\emph{Docker Alpine Linux}. {[}online] 2016 {[}cit. 2017-4-19]. Dostupné z: \url{https://github.com/gliderlabs/docker-alpine#usage}

\bibitem{swarm_arch} Docker Documentation 
	\emph{Docker Documentation:Swarm mode overview}. {[}online] 2016 {[}cit. 2017-3-26]. Dostupné z: \url{https://docs.docker.com/engine/swarm/}
	
\end{thebibliography}
